---
title: "The Report of Steam Game Store"
author: "Jinyu"
date: "12/13/2021"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=5, fig.height=5,fig.align = "center") 
pacman::p_load(
tidyverse,
magrittr,
knitr,
ggplot2
)

source("process_data.R")
```


## Abstract

## Introduction
video games are becoming more and more popular, especially during the pandemic and because of the RTX 30 series of Graphic Cards of Nvidia, which makes games run more smoothly and the graphics even more delicate. Many publishers take the advantage of this and provide their better service to attract people. Consequently, I would like to ask, except for the graphs, what aspects of games make them popular and attract people and I use the data from Steam.

As most of us known, The Steam platform is the largest digital distribution platform for PC gaming, holding around 75% of the market share in 2013. It is run by Valve, providing installations and automatic updates for Valve's games as well as games from third-party publishers and it's a good communities for players to discuss games, where we can find a lot of information whether one game is good or not from customers including their playtime and so on. Therefore, Steam games data are good resource for me to do some analysis. 

To represent the degree of preference towards one game, I would like to use the rating ratio, which is the positive ratings/negative ratings. 

## Method

### Data Cleaning and Processing
The data is from Kaggle, named [Steam Store Games (Clean dataset)](https://www.kaggle.com/nikdavis/steam-store-games). Although the data seem to be clean, but it is not good enough for me to get some usefull information and some columns and words are not machine and human readable. Therefore I need to wrangle my data. First, I extract some information in some columns and make some more dummy variables, for example in the "platforms" column it contains the systems(Linux, Windows, or Mac) that the game supports, I divide them into 3 dummy varibles to show which system is available for one game. Second, I change some variables into values to make them readable. For example, the "owner" column reprents the range of owners for one game like 500000-1000000, and I change them into rank value from 1 to 13 where 1 is the smallest amount of owners for one game. Third, I dropped some columns that I don't need like "appid", "english", etc.

After cleaning the data, I get the data I need for EDA and modeling, which is as follows:
```{r}
df1 <- clean_data()
str(df1)
max(df1$owner_rank)
```


\vspace{0.5cm}

| Column             | Description                                                              |
|:-------------------|:-------------------------------------------------------------------------|
| name               | Title of app (game)                                                      |
| release_date       | Integers, release date for the game, in format YYYY-MM-DD                |
| average_playtime   | Integers, average user playtime, from SteamSpy                           |
| median_playtime    | Integers, median user playtime, from SteamSpy                            |
| price              | Float, Full price of title in GBP in 2019                                |
| platform           | Integers,the number of systems the game supports, integer ranged 1 to 3  |
| rating_ratio       | Float, Positive ratings : Negative ratings                               |
| owner_rank         | Integers, the size of owners, the maximus is 13                          |
| steamspy_tags      | The most correlated genre of the game according to players' views        |
| publisher          | Name of the 1st publisher                                                |
| developer          | Name of the 1st developer                                                |
| multiplayer        | Dummy variables, if the game supports multiplayers                       |
| Windows            | Dummy variables, if the game is available in Windows System              |
| Mac                | Dummy variables, if the game is available in Mac System                  |
| Linux              | Dummy variables, if the game is available in Linux System                |
| Steam_Cloud        | Dummy variables, if the game surports Steam_Cloud                 |
| Anti_Cheat         | Dummy variables, if the game surports Valve Anti-cheat                |
| tags               | The most requently used tags detected in another dataset                 |


### Exploratory Data Analysis

Systems plot
```{r, fig.cap="The Count of Games for different Platforms", fig.height=4, fig.width= 6}
# get the df for platform barplot
df_platform <- data.frame(Count = c(sum(df1$Windows),sum(df1$Linux),sum(df1$Mac)),
                          Platform = c("Windows","Linux","Mac"))
# platform barplot
ggplot(data = df_platform)+
  geom_bar(mapping = aes(x = Platform, y = Count, fill = Platform), stat = "identity") +
  geom_text(mapping = aes(x = Platform, y = Count, label = Count), size = 4)
  
```
Top 10 steam Publishers
```{r fig.cap="Top 10 Steam Publishers", fig.height=4, fig.width= 10}
df1_publisher <- df1 %>% group_by(publisher1) %>% summarise(count_publisher = n())
df1_publisher_tp10 <- df1_publisher[order(-df1_publisher$count_publisher),] %>% head(10)
publisher_tp10 <- df1_publisher_tp10$publisher1
df1_select_pb <- df1 %>% filter(publisher1 %in% publisher_tp10)

ggplot(data = df1_publisher_tp10)+
  geom_bar(mapping = aes(x = publisher1, y = count_publisher, fill = publisher1), stat = "identity")+
  geom_text(mapping = aes(x = publisher1, y = count_publisher, label = count_publisher), size = 4) +
  theme(axis.text.x = element_text(angle = 30))


```
Top 10 steam developers
```{r fig.cap="Top 10 Steam developers", fig.height=4, fig.width= 10}
df1_developer <- df1 %>% group_by(developer1) %>% summarise(count_developer = n())
df1_developer_tp10 <- df1_developer[order(-df1_developer$count_developer),] %>% head(10)
developer_tp10 <- df1_developer_tp10$developer1

# get the top 10 developers in df1
df1_select_pb <- df1 %>% filter(developer1 %in% developer_tp10)

ggplot(data = df1_developer_tp10)+
  geom_bar(mapping = aes(x = developer1, y = count_developer, fill = developer1), stat = "identity")+
  geom_text(mapping = aes(x = developer1, y = count_developer, label = count_developer), size = 4) +
  theme(axis.text.x = element_text(angle = 30))


```

```{r fig.cap="Top 7 rating ratio for Steam Games(app)", fig.height=5, fig.width= 10}
df1_rating_7 <- df1[order(-df1$rating_ratio),] %>% head(7)
df1_rating_7$name[3] <- "Hidden Star in Four Seasons."
df1_rating_7

ggplot(data = df1_rating_7)+
  geom_bar(mapping = aes(x = name, y = rating_ratio, fill = name), stat = "identity")+
  geom_text(mapping = aes(x = name, y = rating_ratio, label = round(rating_ratio, 2)), size = 4) +
  theme(axis.text.x = element_text(angle = 30))


```

median plot
```{r fig.cap="Top 7 median playtime for Steam Games", fig.height=4, fig.width= 10}
df1_median_7 <- df1[order(-df1$median_playtime),] %>% head(7)
# df1_average_10$name[3] <- "Hidden Star in Four Seasons."
df1_median_7

ggplot(data = df1_median_7)+
  geom_bar(mapping = aes(x = name, y = median_playtime, fill = name), stat = "identity")+
  geom_text(mapping = aes(x = name, y = median_playtime, label = round(median_playtime, 2)), size = 4) +
  theme(axis.text.x = element_text(angle = 30))


```

average plot
```{r fig.cap="Top 7 average playtime for Steam Games", fig.height=4, fig.width= 10}
df1_average_7 <- df1[order(-df1$average_playtime),] %>% head(7)
# df1_average_10$name[3] <- "Hidden Star in Four Seasons."


ggplot(data = df1_average_7)+
  geom_bar(mapping = aes(x = name, y = average_playtime, fill = name), stat = "identity")+
  geom_text(mapping = aes(x = name, y = average_playtime, label = round(average_playtime, 2)), size = 4) +
  theme(axis.text.x = element_text(angle = 30))


```

radar plot for top 7 games
```{r fig.cap="Radar charge for Top 7 rating ratio games", fig.height=4, fig.width= 10}
library(fmsb)

select_col <- c("achievements", "median_playtime", "price", "platform1", "log_rating_ratio", "owner_rank")

df_radar_plot <- df1_rating_7 %>% select(select_col)
df_radar_plot <- rbind(apply(df_radar_plot, 2, max),apply(df_radar_plot, 2, min), df_radar_plot)


colors_fill <- c(scales::alpha("darkgoldenrod2",0.1),
                 scales::alpha("aquamarine",0.1),
                 scales::alpha("darkorange2",0.2),
                 scales::alpha("blue1",0.2),
                 scales::alpha("brown2",0.2),
                 scales::alpha("burlywood4",0.2),
                 scales::alpha("chartreuse",0.2),
                 scales::alpha("deeppink2",0.2))
  
# set the radar line color
colors_line <- c(scales::alpha("darkgoldenrod2",0.9),
                 scales::alpha("aquamarine",0.9),
                 scales::alpha("darkorange2",0.9),
                 scales::alpha("blue1",0.9),
                 scales::alpha("brown2",0.9),
                 scales::alpha("burlywood4",0.9),
                 scales::alpha("chartreuse",0.9),
                 scales::alpha("deeppink2",0.9))

# plot the radar chart
radarchart(df_radar_plot,
           seg = 7,
           # title = 
           pcol = colors_line,
           # pfcol = colors_fill,
           plwd = 1)

# add the legend for the radar chart
legend(x=1.8,
       y=1.35,
       legend = df1_rating_7$name,
       bty = "n", pch=20, col=colors_line,cex = 1.2, pt.cex = 3)



```

radar plot separatively
```{r fig.cap="Radar charge for Top 7 rating ratio games seperatively", fig.height=4, fig.width= 10}
library(customLayout)
par(mar = c(1,2,2,1))

lay <- lay_new(matrix(1:9, nc = 3),
               widths = c(2,2,2),
               heights = c(2,2,2))
lay_set(lay)
for (i in 1:(nrow(df_radar_plot)-2)){
  df_radar_plot1 <- df_radar_plot[c(1,2,i+2),]
  # plot the radar chart
  radarchart(df_radar_plot1,
             seg = 4,
             title = df1_rating_7$name[i],
             pcol = colors_line[i],
             pfcol = colors_fill[i],
             plwd = 1)
  # add the legend for the radar chart
  # legend(x=1.8,
  #        y=1.35,
  #        legend = df1_rating_7$name[i],
  #        bty = "n", pch=20, col=colors_line,cex = 1.2, pt.cex = 3)
}


```
radar plot for top 10 companies
```{r fig.cap="Radar charge for Top 7 rating ratio games seperatively", fig.height=4, fig.width= 10}
# get the top 10 developers in df1
## df1_select_pb
colnames(df1_select_pb)

# df1_pb_stat <- df1_select_pb %>% group_by(publisher1) %>% summarise_at(vars(col_1), list(mid_6h = median))



# for (i in 1:(nrow(df_radar_plot)-2)){
#   df_radar_plot1 <- df_radar_plot[c(1,2,3)]
#   # plot the radar chart
#   radarchart(df_radar_plot1,
#              seg = 4,
#              pcol = colors_line,
#              pfcol = colors_fill,
#              plwd = 1)
#   # add the legend for the radar chart
#   legend(x=1.8,
#          y=1.35,
#          legend = df1_rating_7$name,
#          bty = "n", pch=20, col=colors_line,cex = 1.2, pt.cex = 3)
# }

```

Histogram plot
```{r fig.cap="Radar charge for Top 7 rating ratio games", fig.height=5, fig.width= 10}

df1$log_rating_ratio <- log(df1$rating_ratio)
df1$posi_ratio <- (df1$positive_ratings/(df1$positive_ratings+df1$negative_ratings))
df1$log_posi_ratio <- log(df1$positive_ratings/(df1$positive_ratings+df1$negative_ratings))

# ggplot(data = df1, mapping = aes(x = rating_ratio))+
#   geom_histogram(alpha = 0.6)
# 
# ggplot(data = df1, mapping = aes(x = log_rating_ratio))+
#   geom_bar(mapping = aes(fill = "blue"),stat = "count", position = "dodge", alpha = 0.6, width = 2)

## best 
ggplot(data = df1, mapping = aes(x = log_rating_ratio))+
  # geom_bar(mapping = aes(fill = "blue"),stat = "count", position = "dodge", alpha = 0.6, width = 2) +
  geom_histogram(mapping = aes(fill = "red"),alpha = 0.6)

##

# ggplot(data = df1, mapping = aes(x = rating_ratio))+
#   geom_bar(stat = "count", position = "dodge", alpha = 0.6, width = 2)
# 
# ggplot(data = df1, mapping = aes(x = posi_ratio, fill = "green"))+
#   geom_bar(stat = "count", position = "dodge", alpha = 0.6, width = 2)




```

Histogram plot for top10 publishers
```{r fig.cap="Radar charge for Top 7 rating ratio games", fig.height=5, fig.width= 10}
ggplot(data = df1_select_pb, mapping = aes(x = log_rating_ratio, fill = publisher1))+
  # geom_bar(mapping = aes(fill = "blue"),stat = "count", position = "dodge", alpha = 0.6, width = 2) +
  geom_histogram(mapping = aes(fill = "red"),alpha = 0.6) +
  facet_wrap(~publisher1) +
  ggtitle("log(rating_ratio) distribution for top10 publishers")
```


### Model Fitting

## Result

## Discussion

## Reference
1. [Steam wikipedia](https://en.wikipedia.org/wiki/Steam_(service))

2.[Steam Store Games (Clean dataset)](https://www.kaggle.com/nikdavis/steam-store-games)

\newpage

## Appendix
